A Kochen-Specker system has at least 22 vertices

### 2014-04-08 main.tex
Improve abstract

    Continuing their effort, we restrict our enumeration to smaller class of
    graphs and develop a practical decision procedure for embeddability, to
    establish an improved lower bound of 22.
\end{abstract}

>>>>

    Continuing their effort, we restrict our enumeration to smaller class of
    graphs and develop a practical decision procedure for embeddability, to
    improve the lower bound to 22.
\end{abstract}
